Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/30-dataset.tex
French goes in italic

Directories contain lists of people with various information attached.
For instance the directory published by \emph{Didot} in 1854 contains three redundant lists or people sorted by name, by activity and by street name.
An typical example entry from this directory is "Batton (D.-A.) \scalerel*{\includegraphics{./images/LH.png}}{H}, professeur au Conservatoire de musique et de déclamation, Saint-Georges, 47.":  it begins with the person's name and surname (here in parentheses).
The glyph denotes that this person was awarded the Légion d'Honneur.
Then comes a descriptions of the person's activity, here his profession (professor at the Conservatory of music and declamation), but it can also be a social status.
Such descriptions range from a single word to paragraphs describing the occupation in full detail.
The street name and number where the person lives or carries out their activities ends the entry.

>>>>

Directories contain lists of people with various information attached.
For instance the directory published by \emph{Didot} in 1854 contains three redundant lists of people sorted by name, by activity and by street name.
An typical example entry from this directory is "\textit{Batton (D.-A.) \scalerel*{\includegraphics{./images/LH.png}}{H}, professeur au Conservatoire de musique et de déclamation, Saint-Georges, 47.}".
It begins with the person's name and surname, here inside parentheses.
The glyph denotes that this person was awarded the \textit{Légion d'Honneur}.
Then comes a descriptions of the person's activity, here his profession (professor at the Conservatory of music and declamation), but it can also be a social status.
Such descriptions range from a single word to paragraphs describing the occupation in full detail.
The street name and number where the person lives or carries out their activities ends the entry.

### 2022-01-20 src-latex/parts/60-ner-xp2-pretraining-and-finetuning.tex
Part 3 shorter (i guess ?)
French goes in italic

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{images/experiment_2_f1_with_noise_graph.pdf}
    \caption{\label{fig:exp_2_eval_ner}NER F1-scores in presence of OCR noise in the training and testing examples, grouped by test set. The dataset used to train the NER task is noted in indice after the model name (e.g. CmBERT$_{pero}$ means CmBERT fine-tuned on NER-\emph{pero}).}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{images/experiment_2_f1_with_noise_graph.pdf}
    \caption{\label{fig:exp_2_eval_ner}NER F1-scores in presence of OCR noise in the training and testing sets, grouped by test set. The dataset used for training is noted in indice after the model name (e.g. CmBERT$_{pero}$ means CmBERT fine-tuned on NER-\emph{pero}).}
\end{figure}
